Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-21 article_review/Manuscript.tex
More changes

A practical problem concerning the use of these methods is how to quantify the number of model evaluations required to ensure that Sobol' estimates are accurate enough. This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences. The error bound is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition. We propose a sequential estimation procedure of Sobol' indices using the error bound as our stopping criterion. The procedure operates under the assumption that all integrands lie inside a particular cone of functions (see \cite{HicJim}).

@@

%The problem of interest is the evaluation of first-order and total effect Sobol' indices.
In our framework, we are only interested in single input indices, namely $|u|=1$. The computation of the normalized indices is performed based on the following integral formulas for their numerators:
{\color{purple}(Lolo)
\begin{align}
\label{first.order}
\underline{\tau}_u^2  &= \int_{[0,1]^{2d}} \left(
f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}, \\
\label{total.effect}
\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1]^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d\vx_u d{\vx'}, \ u \in \mathcal{D},
\end{align}
}
while variance and mean of $f$ are evaluated as:
\begin{gather}
\begin{aligned}
\sigma^2 &= \int_{[0,1]^{d}} f(\vx)^2d{\vx} - \mu^2, \\
 \mu &= \int_{[0,1]^{d}} f(\vx) d{\vx},
\label{eq.sigma.mu}
\end{aligned}
\end{gather}
Usually the complexity of $f$ causes the solution of integrals \eqref{first.order}, (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable. In such cases, one can instead estimate these quantities.

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
{\color{purple}(Lolo)
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_{i,u}:{\vx'}_{i,-u})-f(\vx'_i)\right)f(\vx_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
}
using for $\sigma^2$:
{\color{purple} (Lolo)
\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{n-1} \sum \limits_{i=0}^{n-1} \left( f(\vx_i) - \widehat{\mu}\right)^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
\label{mu.est}
\end{equation}
}
Then, the Sobol' indices estimators are:
\begin{equation}
\widehat{\underline{S}}_u = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
\widehat{\overline{S}}_u = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
\label{common.sobol.est}
\end{equation}
Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$. Thus, for all first order and total effect indices, one would need $3nd$ model evaluations. Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The main idea of the theorem is that there is no need to reevaluate $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$. Hence, we can simply evaluate $f({\vx}_i)$ $n$ times, $f({\vx'}_i)$ $n$ times, and $f(\vx_{i,u}:{\vx'}_{i,-u})$ $nd$ times, which accounts for the $n(d+2)$ evaluations.

@@

{\color{purple} (Lolo) 
\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1]^{d}$. In these sets, all points $\vx_i$ (resp. $\vx'_i$) are coordinate-wise different, i.e. for all $(i_1,i_2) \in \{0,\dots,n-1\}^2$ such that $i_1 \neq i_2$: $$x_{i_1,j} \neq x_{i_2,j}, \qquad \text{for any  } j=1,\dots,d .$$
Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$. We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$ and exclude the trivial case $\vx_i = \vx'_i$ for all $i\in\{0,\dots,n-1\}$.
\end{definition}
}

@@

\comment{For this sequence of digital nets,} each $\mathcal{P}_m$ has a group structure under the digitwise addition:
\[
\vx \oplus \vt = \left(\sum_{\ell=1}^{\infty} [(x_{j\ell} + t_{j\ell}) \bmod b] b^{-\ell} \pmod{1} \right)_{j=1}^d,
\]
where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$,\comment{ i.e.
\[
x_{j} = \sum_{\ell=1}^{\infty} x_{j\ell}b^{-\ell},\qquad t_{j} = \sum_{\ell=1}^{\infty} t_{j\ell}b^{-\ell}.
\]
For $b=2$, the digitwise addition is equivalent to the XOR operation.

@@

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
In this section we will extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To achieve this goal, we consider the two integral formulas of the first-order and total effect Sobol' indices with $|u|=1$:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
{\color{purple}(Lolo)
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with known error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$, $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.

@@

Algorithm \ref{recursive.algorithm} summarizes the main steps of our sequential procedure. First, one must fix the tolerance $\epsilon >0$ at which Sobol' indices must be estimated, and set $m=\ell_*+r$, where $\ell_*$ and $r$ are the two hyper-parameters defined in \eqref{conecond}.  {\color{purple} (Lolo) The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).}

Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}. {\color{purple} (Lolo) This approach iteratively constructs a $2d$-dimensional Sobol' sequence then assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$. The $2d$-dimensional Sobol' sequence is generated based on the direction numbers found in \cite{Kuo}. These direction numbers optimize the two-dimensional projections of the Sobol' sequence. Although this is the authors choice, one may choose any other Sobol' construction of $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ as long as the $2d$ dimensions are each generated with different primitive polynomials. In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.}

@@

Alternatively, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with the replication procedure to estimate all first-order Sobol' indices. This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}. {\color{purple} (Lolo) However, in this case, the scrambling applied to both designs must be identical to insure that $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are replicated designs of order one.}

@@

\hspace*{-0.3cm} $\mathcal{P}'_m \leftarrow \mathcal{P}'_{m-1} \cup {B'}_m$
\For {$u =1,\dots,d$}
\If {Variant $A$}
\If {$! bool_u$}
\State compute $\widehat{\underline{S}}_u$ and $\widehat{\ov{$S$}}_u$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}), and Saltelli's strategy
\State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon \ \& \ \varepsilon_{\widehat{\widehat{\overline{S}}}_u} \leq \epsilon$
\State $m_u \leftarrow m$
\EndIf
\EndIf
\If {Variant $B$}
\If {$! bool_u$}
\State estimate $\widehat{\underline{S}}_u$ with formula (\ref{formula_undersu}) and the replication procedure
\State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon$
\State $m_u \leftarrow m$
\EndIf
\EndIf
\EndFor
\State $bool \leftarrow \forall u: \ bool_u$
\State $m \leftarrow m + 1$
\EndWhile
\State return the Sobol' estimates.
\end{algorithmic}
\label{recursive.algorithm}
\end{algorithm}
\bigskip

@@

When $\underline{S}_u$ is small, it usually becomes harder to estimate. For this reason, we consider the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator called ``Correlation 2" has been introduced by Owen in \cite{Owen}. In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices. Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple} (Lolo) improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
\begin{equation*}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)).
\end{equation*}
\comment{As proposed by Owen in \cite{Owen}, the sample points are $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. For our algorithm, we extend Owen's estimator by replacing the uniform points with a Sobol' sequence in dimension $3d$. In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.}
\bigskip

@@

In practice, one does not know which are the small Sobol' indices ($u_1,\dots,u_\gamma)$. To overcome this issue, we propose the following alternative for Variant $A$. {\color{purple}(Lolo) If at the end of the first iteration $\widehat{\underline{S}}_u$ is smaller than a threshold (in our case $0.1$, as suggested by Owen), the estimator (\ref{first.order.est}) is switched to ``Correlation 2" for this particular $u$. Then, a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$. $\mathcal{P''}$ is obtained by assigning and scrambling the next $d$ coordinates of the starting $2d$-dimensional Sobol' sequence.}

@@

For the two test functions, results of the three variants are compared based on the true estimation errors. These errors correspond to the absolute difference between the true values and their estimates:
$$\delta_{\underline{S}_u} = \absolute{\underline{S}_u - \widehat{\underline{S}_u}}, \qquad \delta_{\overline{S}_u} = \absolute{\overline{S}_u - \widehat{\overline{S}_u}}.$$
{\color{purple} (Lolo) True values of Sobol' indices are estimated with a precision of $10$ digits. For clarity concern, they are rounded in the tables presenting the results.}

We also compare the total number of evaluations of each variant. {\color{purple} (Lolo) Results are averaged over $100$ repetitions by applying different scrambling}. For each repetition, we fix the tolerance $\varepsilon=5\cdot10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points). The algorithm error bound factor described in \eqref{errbd} is set to $\mathfrak{C}(m)=10\times 2^{-m}$.

\comment{For the examples in this section we do not know the true Walsh coefficients of the integrands. Indeed, since the mapping $\tilde{\vk}$ is chosen heuristically, the cone conditions will also depend on each scrambling. Therefore, we cannot say whether the integrands lie inside the cone. For this reason, we define the failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$ over the $100$ repetitions. These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$. When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and at least one integrand ($I_1$, $I_2$, $I_3$, or $I_4$) falls outside the cone \eqref{conecond}.}

%{\color{purple} (Lolo) To test if the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$,

@@

The two classical test functions considered in this article are {\color{purple} (Lolo) a non qMC friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}. The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).

@@

As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower estimation errors for these four inputs. The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4} \sim 10^{-5}$).

>>>>

A practical problem concerning the use of these methods is how to quantify the number of model evaluations required to ensure that Sobol' estimates are accurate enough. This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences. \comment{One reason to use digital sequences is that the numerical integration convergence rates are of $\mathcal{O}(n^{-1+\delta})$ ($n$ being the number of function values) instead of the usual $\mathcal{O}(n^{-1/2})$ for iid Monte Carlo methods. In addition,} the error bound in this article is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition. We propose a sequential estimation procedure of Sobol' indices using the error bound as our stopping criterion. The procedure operates under the assumption that all integrands lie inside a particular cone of functions (see \cite{HicJim}).

@@

%The problem of interest is the evaluation of first-order and total effect Sobol' indices.
In our framework, we are only interested in single input indices, namely $|u|=1$. The computation of the normalized indices is performed based on the following integral formulas for their numerators:
{\color{purple}
\begin{align}
\label{first.order}
\underline{\tau}_u^2  &= \int_{[0,1]^{2d}} \left(
f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}, \\
\label{total.effect}
\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1]^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d\vx_u d{\vx'}, \ u \in \mathcal{D},
\end{align}
}
while variance and mean of $f$ are evaluated as:
\begin{gather}
\begin{aligned}
\sigma^2 &= \int_{[0,1]^{d}} f(\vx)^2d{\vx} - \mu^2, \\
 \mu &= \int_{[0,1]^{d}} f(\vx) d{\vx},
\label{eq.sigma.mu}
\end{aligned}
\end{gather}
Usually the complexity of $f$ causes the solution of integrals \eqref{first.order}, (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable. In such cases, one can instead estimate these quantities.

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
{\color{purple}
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_{i,u}:{\vx'}_{i,-u})-f(\vx'_i)\right)f(\vx_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
}
using for $\sigma^2$:
{\color{purple} 
\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{n-1} \sum \limits_{i=0}^{n-1} \left( f(\vx_i) - \widehat{\mu}\right)^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
\label{mu.est}
\end{equation}
}
Then, the Sobol' indices estimators are:
\begin{equation}
\widehat{\underline{S}}_u = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
\widehat{\overline{S}}_u = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
\label{common.sobol.est}
\end{equation}
Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$. Thus, for all first order and total effect indices, one would need $3nd$ model evaluations. Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The main idea of the theorem is that there is no need to reevaluate $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$. Hence, we can simply evaluate $f({\vx}_i)$ $n$ times, $f({\vx'}_i)$ $n$ times, and $f(\vx_{i,u}:{\vx'}_{i,-u})$ $nd$ times, which accounts for the $n(d+2)$ evaluations.

@@

{\color{purple}  
\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1]^{d}$. In these sets, all points $\vx_i$ (resp. $\vx'_i$) are coordinate-wise different, i.e. for all $(i_1,i_2) \in \{0,\dots,n-1\}^2$ such that $i_1 \neq i_2$: $$x_{i_1,j} \neq x_{i_2,j}, \qquad \text{for any  } j=1,\dots,d .$$
Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$. We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$ and exclude the trivial case $\vx_i = \vx'_i$ for all $i\in\{0,\dots,n-1\}$.
\end{definition}
}

@@

\comment{For this sequence of digital nets,} each $\mathcal{P}_m$ has a group structure under the digitwise addition:
\[
\vx \oplus \vt = \left(\sum_{\ell=1}^{\infty} [(x_{j\ell} + t_{j\ell}) \bmod b] b^{-\ell} \pmod{1} \right)_{j=1}^d,
\]
where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$, \comment{ i.e.
\[
x_{j} = \sum_{\ell=1}^{\infty} x_{j\ell}b^{-\ell},\qquad t_{j} = \sum_{\ell=1}^{\infty} t_{j\ell}b^{-\ell}.
\]
For $b=2$, the digitwise addition is equivalent to the XOR operation.

@@

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
In this section we will extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To achieve this goal, we consider the two integral formulas of the first-order and total effect Sobol' indices with $|u|=1$:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
{\color{purple}
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1]^{2d}} \left(f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}}{\int_{[0,1]^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1]^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1]^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1]^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1]^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with known error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$, $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.

@@

Algorithm \ref{recursive.algorithm} summarizes the main steps of our sequential procedure. First, one must fix the tolerance $\epsilon >0$ at which Sobol' indices must be estimated, and set $m=\ell_*+r$, where $\ell_*$ and $r$ are the two hyper-parameters defined in \eqref{conecond}.  {\color{purple}  The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})). Parameter $r$ should also be chosen carefully: larger values of $r$ will imply a smaller error bound and more dependence on smaller Walsh coefficients, while smaller of values of $r$ might incur in aliasing errors.}

Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}. {\color{purple}  This approach iteratively constructs a $2d$-dimensional Sobol' sequence. Then, it assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$. The $2d$-dimensional Sobol' sequence is generated based on the direction numbers found in \cite{Kuo}. These direction numbers optimize the two-dimensional projections of the Sobol' sequence. Although this is the authors choice, one may choose any other Sobol' construction for $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ as long as the $2d$ dimensions are each generated with different primitive polynomials. In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling \cite{HonHic00a,Owe95}.}

@@

Alternatively, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with the replication procedure to estimate all first-order Sobol' indices. This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}. {\color{purple}  In this case, the scrambling applied to both designs must be identical to ensure that $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are replicated designs of order one.}

@@

\hspace*{-0.3cm} $\mathcal{P}'_m \leftarrow \mathcal{P}'_{m-1} \cup {B'}_m$
\For {$u =1,\dots,d$}
\If {Variant $A$}
\If {$! bool_u$}
\State compute $\widehat{\underline{S}}_u$ and $\widehat{\ov{$S$}}_u$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}), and Saltelli's strategy
\State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon \ \& \ \varepsilon_{\widehat{\overline{S}}_u} \leq \epsilon$
\State $m_u \leftarrow m$
\EndIf
\EndIf
\If {Variant $B$}
\If {$! bool_u$}
\State estimate $\widehat{\underline{S}}_u$ with formula (\ref{formula_undersu}) and the replication procedure
\State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon$
\State $m_u \leftarrow m$
\EndIf
\EndIf
\EndFor
\State $bool \leftarrow \forall u: \ bool_u$
\State $m \leftarrow m + 1$
\EndWhile
\State return the Sobol' estimates.
\end{algorithmic}
\label{recursive.algorithm}
\end{algorithm}
\bigskip

@@

When $\underline{S}_u$ is small, it usually becomes harder to estimate. For this reason, we consider the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator called ``Correlation 2" has been introduced by Owen in \cite{Owen}. In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices. Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple}  improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
\begin{equation*}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)).
\end{equation*}
\comment{As proposed by Owen in \cite{Owen}, the sample points are $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. For our algorithm, we extend Owen's estimator by replacing the uniform points with a scrambled Sobol' sequence in dimension $3d$. In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.}
\bigskip

@@

In practice, one does not know which are the small Sobol' indices ($u_1,\dots,u_\gamma)$. To overcome this issue, we propose the following alternative for Variant $A$. {\color{purple} If at the end of the first iteration $\widehat{\underline{S}}_u$ is smaller than a threshold (in our case $0.1$, as suggested by Owen), then the estimator (\ref{first.order.est}) is switched to ``Correlation 2" for this particular $u$. In this case, a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$. $\mathcal{P''}$ can be generated assigning and scrambling the last $d$ coordinates of a $3d$-dimensional Sobol' sequence.}

@@

For the two test functions, the results of the three variants are compared based on the true estimation errors. These errors correspond to the absolute difference between the true values and their estimates:
$$\delta_{\underline{S}_u} = \absolute{\underline{S}_u - \widehat{\underline{S}_u}}, \qquad \delta_{\overline{S}_u} = \absolute{\overline{S}_u - \widehat{\overline{S}_u}}.$$
{\color{purple} The true values of Sobol' indices are estimated with a precision of $10$ digits. For clarity purposes, in the following tables all results are rounded to $4$ digits.}

We also compare the total number of evaluations of each variant to verify the assumption in Section \ref{sec:4.2}. {\color{purple}  Results are averaged over $100$ repetitions, each computed with different random scramblings}. For all repetitions, we fix the tolerance $\varepsilon=5\cdot 10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points). The error bound factor described in \eqref{errbd} is set to $\mathfrak{C}(m)=10\times 2^{-m}$.

\comment{For these examples we do not know the true Walsh coefficients of the integrands. Indeed, since the mapping $\tilde{\vk}$ is chosen heuristically, the cone conditions will also depend on each scrambling. Therefore, we cannot say whether the integrands lie inside the cone. For this reason, we define the failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$ over the $100$ repetitions. These rates are the proportion of the repetitions in which the true errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\overline{S}_u} \leq \varepsilon$. When $\delta_{\underline{S}_u} > \varepsilon$ or $\delta_{\overline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and at least one integrand ($I_1$, $I_2$, $I_3$, or $I_4$) falls outside the cone \eqref{conecond}.}

%{\color{purple}  To test if the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$,

@@

The two classical test functions considered in this article are {\color{purple} a non qMC (quasi-Monte Carlo) friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}. The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).

@@

As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower estimation errors for these four inputs. The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4}$ to $10^{-6}$).
